### 2021-04-26 input/introduction.tex
wip

In this paper, we first define scoped broadcast as a communication
primitive that allows epidemic dissemination of messages as long as
receiving \processes verify an application-dependant predicate.  Then,
we propose \emph{\NAME}, a logical partitioning protocol that uses
\underline{s}coped broad\underline{cast} to \underline{a}dapt its
partitions, \ie scopes, to creations and deletions of partitions in
the system. Each source advertises its existence to all possibly
interested \processes, \ie only interconnected \processes of its
partition plus \processes bordering its partition. In turns, \NAME
scales well to the number of sources since the higher the number of
partitions, the earlier the dissemination stops.
%
%% In this paper, we propose a first implementation of such a protocol.
%% Entitled Adaptive Scoped broadcast (\NAME), 
%% our protocol relies on a primitive that forwards
%% messages until a certain condition is reached, \ie the scope. The
%% scope is defined by a boolean function (predicate) that returns
%% whether a message should be propagated or not around its
%% broadcaster. In the current scenario, the stop condition is related to
%% the distance to the nearest replica : if the message that a node receives
%% indicates a content has a longer distance than that which the node
%% knows then the transfer of the message is useless and so stopped.
%

>>>>

\noindent The contribution of this paper is threefold:

\begin{asparadesc} %% to remove left-margin :p
\item [$\bullet$] We highlight the properties that guarantee
  decentralized consistent partitioning in dynamic infrastructures. We
  demonstrate that concurrent creation and removal of partitions may
  impair the propagation of control information crucial for consistent
  partitioning. Yet, \processes are able to purge stale information
  forever using only neighbor-to-neighbor communication, hence leaving
  room for up-to-date information propagation, and eventually
  consistent partitioning.
\item [$\bullet$] We provide an implementation entitled \NAME that
  uses aforementioned principles to \underline{a}dapt its
  partitioning, \ie \underline{s}copes, to creations and deletions of
  partitions in the system. \NAME relies on a communication primitive
  \underline{s}coped-broad\underline{cast} as \TODO{a communication
    primitive that allows epidemic dissemination of messages as long
    as receiving \processes verify an application-dependant
    predicate.}

\end{asparadesc}

%% Then, we propose \emph{\NAME}, a logical partitioning protocol that
%% uses \underline{s}coped broad\underline{cast} to \underline{a}dapt its
%% partitions, \ie scopes, to creations and deletions of partitions in
%% the system. Each source advertises its existence to all possibly
%% interested \processes, \ie only interconnected \processes of its
%% partition plus \processes bordering its partition. In turns, \NAME
%% scales well to the number of sources since the higher the number of
%% partitions, the earlier the dissemination stops.

%
%% In this paper, we propose a first implementation of such a protocol.
%% Entitled Adaptive Scoped broadcast (\NAME), 
%% our protocol relies on a primitive that forwards
%% messages until a certain condition is reached, \ie the scope. The
%% scope is defined by a boolean function (predicate) that returns
%% whether a message should be propagated or not around its
%% broadcaster. In the current scenario, the stop condition is related to
%% the distance to the nearest replica : if the message that a node receives
%% indicates a content has a longer distance than that which the node
%% knows then the transfer of the message is useless and so stopped.
%
